Forecasting the 2024 U.S. Presidential Election: Polling Trends and Dynamics Based on National General Election Polls

### 2024-11-04 paper/paper.qmd
Test

Figure 2.2 displays the percentage support for each candidate across different states. This visualization helps identify regional strengths and weaknesses for both candidates, providing a more granular view of voter sentiment.

>>>>

Figure 2.2 displays the percentage support for each candidate across different states. This visualization helps identify regional strengths and weaknesses for both candidates, providing a more granular view of voter sentiment.
```{r}
#| warning: false
#| message: false
#| echo: false

if (!require(usmap)) install.packages("usmap")
if (!require(ggplot2)) install.packages("ggplot2")
if (!require(dplyr)) install.packages("dplyr")
if (!require(readr)) install.packages("readr")
state_support_stats <- read_parquet(here("data/04-electoral_college_estimate/states_support.parquet"))
winners <- state_support_stats %>%
  group_by(state) %>%
  filter(avg_support == max(avg_support)) %>%
  ungroup()

# Convert state names to abbreviations (required by usmap)
winners$abbr <- state.abb[match(winners$state, state.name)]

all_states <- state.name

# Find the states present in the winners data
states_in_winners <- unique(winners$state)

# Find the missing states by comparing with the list of all states
missing_states <- setdiff(all_states, states_in_winners)

# Create a data frame for the missing states with "Uncertainty" as the candidate
missing_states_df <- data.frame(
  state = missing_states,
  candidate_name = "Uncertainty",
  avg_support = NA,  # Since we don't have support data for missing states
  sd_support = NA,
  electoral_votes = NA,
  abbr = state.abb[match(missing_states, state.name)] # Add state abbreviations
)

# Add the missing states to the winners dataset
winners <- bind_rows(winners, missing_states_df)

# Change Nebraska's candidate to "Uncertainty" for all entries
winners <- winners %>%
  mutate(candidate_name = ifelse(state == "Nebraska", "Uncertainty", candidate_name))

# Remove duplicate entries for Nebraska, keeping only one
winners <- winners %>%
  distinct(state, .keep_all = TRUE)

plot_usmap(data = winners, values = "candidate_name", regions = "states") +
  scale_fill_manual(values = c("Donald Trump" = "red", "Kamala Harris" = "blue", "Uncertainty" = "grey")) +
  labs(title = "2024 U.S. Presidential Election: State Winners",
       fill = "Candidate") +
  theme(legend.position = "right")
